# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

This code loads the csv file:
```{r loadCSV}
data<-read.csv("activity.csv")
```


## What is mean total number of steps taken per day?

First we calculate the total number of steps per day ignoring the NA values:
```{r totalSteps}
spd <- sapply(split(data$steps, data$date, drop=TRUE), sum)
```

Now the histogram is drawn using the ggplot2 library, the frequency is calculated
for intervals of 1000 steps:
```{r histogram}
library(ggplot2)
qplot(spd, xlab="Total number of steps per day",breaks=seq(0, 20000, by=1000))
```

This code calculates the mean and the median for the daily totals:
```{r meanAndMedian}
mean.spd <- format(mean(spd,na.rm=TRUE),scientific = FALSE)
median.spd <- format(median(spd,na.rm=TRUE),scientific = FALSE)
```

The mean for the total number of steps per day is `r mean.spd` steps and the median
is `r median.spd` steps.


## What is the average daily activity pattern?

```{r}
```

## Imputing missing values

```{r}
```

## Are there differences in activity patterns between weekdays and weekends?
```{r}
```