# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

This code loads the csv file:
```{r loadCSV}
data<-read.csv("activity.csv")
```


## What is mean total number of steps taken per day?

First we calculate the total number of steps per day ignoring the NA values:
```{r totalSteps}
spd <- sapply(split(data$steps, data$date, drop=TRUE), sum)
```

Now the histogram is drawn using the ggplot2 library, the frequency is calculated
for intervals of 1000 steps:
```{r histogram}
library(ggplot2)
qplot(spd, xlab="Total number of steps per day",breaks=seq(0, 20000, by=1000))
```

This code calculates the mean and the median for the daily totals:
```{r meanAndMedian}
mean.spd <- format(mean(spd,na.rm=TRUE),scientific = FALSE)
median.spd <- format(median(spd,na.rm=TRUE),scientific = FALSE)
```

The mean for the total number of steps is `r mean.spd` steps and the median
is `r median.spd` steps.


## What is the average daily activity pattern?

This is the calculation of the averages by interval:

```{r averageActivity}
avg.interval <- sapply(split(data$steps,data$interval),function(x) 
                        {mean(x,na.rm=TRUE)})

time.max.avg <- names(sort(avg.interval, decreasing=TRUE)[1])
max.avg <- sort(avg.interval, decreasing=TRUE)[[1]]
```

The plot of averages by interval:
```{r intervalPlot}
plot(names(avg.interval),avg.interval,type="l",xlab="Time interval", ylab="steps")
```

The maximum average number of steps occur at `r time.max.avg` with `r max.avg` steps.

## Imputing missing values

Total number of missing values:
```{r}
total.na<-length(which(is.na(data)))

record.mean<- mean(data$steps, na.rm=TRUE)
```

1. There are `r total.na` records with missing values.

2. The strategy will be to replace these NA values with the average number of 
  steps (`r record.mean`)

3. The new dataset will be called **data.wo.na**

4. Now we plot the same histogram on the modified data:

```{r}
data.wo.na<-data
data.wo.na$steps[which(is.na(data.wo.na$steps))] <- record.mean
```

```{r histogram2}
spd.wo.na <- sapply(split(data.wo.na$steps, data.wo.na$date, drop=TRUE), sum)
qplot(spd.wo.na, xlab="Total number of steps per day",breaks=seq(0, 20000, by=1000))
mean.spd.wo.na <- format(mean(spd.wo.na),scientific = FALSE)
median.spd.wo.na <- format(median(spd.wo.na),scientific = FALSE)
```

The mean for the total number of steps was `r mean.spd` steps, now it is 
still `r mean.spd.wo.na`.  The median was `r median.spd` steps after 
replacing the NA values it becomes `r median.spd.wo.na`, these values don't 
change much as the mean and the median were already very close.

The effect of the replacement of the NA values is a higher count of average 
days, lower and higher days remain mostly unchanged.

## Are there differences in activity patterns between weekdays and weekends?
```{r}
```